Efficient Management of Reified Statements in RDF

### 2012-06-06 paper-iswc-reification/commands.tex
added projection operation to the SPARQL fragment we focus on; started to draft the RDF-compatible semantics for our SPARQL extension
added vars+(tp)
added macros for Reifi and Reifi*
some polishing in Sec.5.3

\newcommand{\RDFplus}{RDF\xxxPLUS}
\newcommand{\SPARQLplus}{SPARQL\xxxPLUS}

@@

\newcommand{\symDescentFct}{\mathrm{rdf}} % the name used for \fctDescent
\newcommand{\fctDescent}[1]{\symDescentFct(#1)} % set of RDF triples for an RDF+ triple/graph

@@

\newcommand{\OpAND}{\text{ \normalfont\scriptsize\textsf{AND} }}
\newcommand{\OpUNION}{\text{ \normalfont\scriptsize\textsf{UNION} }}
\newcommand{\OpOPT}{\text{ \normalfont\scriptsize\textsf{OPT} }}
\newcommand{\OpFILTER}{\text{ \normalfont\scriptsize\textsf{FILTER} }}
\newcommand{\OpAS}{\text{ \normalfont\scriptsize\textsf{AS} }}
\newcommand{\compatible}{\sim} % the symbol for compatibility between valuations
\newcommand{\fctEval}[2]{[\![#1]\!]_{#2}} % the symbol for the evaluation of SPARQL pattern #1 over an RDF graph #2

>>>>

\newcommand{\Reifi}{Reifi}
\newcommand{\ReifiPlus}{Reifi\xxxPLUS}
\newcommand{\RDFplus}{RDF\xxxPLUS}
\newcommand{\SPARQLplus}{SPARQL\xxxPLUS}

@@

\newcommand{\symVarsPlusFct}{\mathrm{vars}^+} % the name used for \fctVarsPlus
\newcommand{\fctVarsPlus}[1]{\symVarsPlusFct\!(#1)} % the set of all variables in pattern #1 and its embedded patterns

\newcommand{\symDescentFct}{\mathrm{rdf}} % the name used for \fctDescent
\newcommand{\fctDescent}[1]{\symDescentFct(#1)} % set of RDF triples for an RDF+ triple/graph
\newcommand{\fctDescentWP}[2]{\symDescentFct^{#1}\!(#2)} % the #1-based, RDF compatible expression of #2

@@

\newcommand{\OpAND}{\text{ \normalfont\scriptsize\textsf{AND} }}
\newcommand{\OpUNION}{\text{ \normalfont\scriptsize\textsf{UNION} }}
\newcommand{\OpOPT}{\text{ \normalfont\scriptsize\textsf{OPT} }}
\newcommand{\OpFILTER}{\text{ \normalfont\scriptsize\textsf{FILTER} }}
\newcommand{\OpAS}{\text{ \normalfont\scriptsize\textsf{AS} }}
\newcommand{\OpSELECT}{\text{\normalfont\scriptsize\textsf{SELECT}}}
\newcommand{\compatible}{\sim} % the symbol for compatibility between valuations
\newcommand{\fctEvalPlus}[2]{[\![#1]\!]^\star_{#2}} % the symbol for the evaluation of SPARQL* pattern #1 over an RDF* graph #2
\newcommand{\fctEval}[2]{[\![#1]\!]_{#2}} % the symbol for the evaluation of SPARQL pattern #1 over an RDF graph #2
